Fusion Moves for Correlation Clustering

### 2014-11-14 paper/anytimefigure2.tex
work on exp sec
update
pimp fig 9
fixed all changes where i knew the fix up tp parameter choise

  restrict y to domain=-40000:-24000,

@@

@@

@@

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPosition}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    % image seg
    %For the image-seg instances in fig.~\ref{fig:at:image-seg} 
    %Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
    %almost the same results, but a bit slower then with EHC proposals.
    %Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
    %leads to suboptimal results.
  %
    %Global optimal methods (MC-I) and the relaxed version (MC-R) are 
    %still usable fast for these instances.
    %% 3d 
    %For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
    %except ??? and EHC perform equally, and the proposed fusion algorithms
    %give the best any time performance.
    %
    %% social nets
    %For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
    %Fusion-HC-MC and Fusion-HC-CGC perform equally.
    %Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
    %fail to converge within this time limit.
    %%%%%
    Among all proposed solvers, Fusion-HC-MC has the best
    overall anytime performance.
    %
    With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
    the runtime of MC-I, MC-R and CGC increases drastically, while
    the proposed solvers still scale well.
    For these instances, the EHC started version of CGC outperforms 
    GCG in terms of runtime and energy.
    %% summary
    \newline
    Overall, energy hierarchical clustering based proposals work better
    then watershed based proposals. They converge to similar energies
    but the clustering based approach is faster on all tested instances.
    On all instances except for modularity clustering, it is better
    to solve the fusion move to optimality (Fusion-HC-MC) then using approximations (FUSION-HC-GCG).
    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
    but both are outperformed by the proposed algorithms w.r.t. any time performance.
    % modularity clustering 
    \newline
    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
    best performance.
    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

  %restrict y to domain=-40000:-24000,

@@

  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-300.data};          \addlegendentry{PIVOT-BOEM}  

@@

  {\color{gray}\hspace{1cm}\rule{0.939\textwidth}{1pt}}\vspace{0.2cm}

@@

  {\color{gray}\hspace{1cm}\rule{0.93\textwidth}{1pt}}\vspace{0.2cm}

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPosition}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    % image seg
    %For the image-seg instances in fig.~\ref{fig:at:image-seg} 
    %Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
    %almost the same results, but a bit slower then with EHC proposals.
    %Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
    %leads to suboptimal results.
  %
    %Global optimal methods (MC-I) and the relaxed version (MC-R) are 
    %still usable fast for these instances.
    %% 3d 
    %For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
    %except ??? and EHC perform equally, and the proposed fusion algorithms
    %give the best any time performance.
    %
    %% social nets
    %For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
    %Fusion-HC-MC and Fusion-HC-CGC perform equally.
    %Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
    %fail to converge within this time limit.
    %%%%%
    Among all proposed solvers, Fusion-HC-MC has the best
    overall anytime performance.
    %
    With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
    the runtime of MC-I, MC-R and CGC increases drastically, while
    the proposed solvers still scale well.
    For these instances, the EHC started version of CGC outperforms 
    GCG in terms of runtime and energy.
    %% summary
    \newline
    Overall, energy hierarchical clustering based proposals work better
    than watershed based proposals. They converge to similar energies
    but the clustering based approach is faster on all tested instances.
    On all instances except for modularity clustering, it is better
    to solve the fusion move to optimality (Fusion-HC-MC) than using approximations (FUSION-HC-GCG).
    The warm EHC started version of GCG (EHC-CGC) performs better than GCG itself,
    but both are outperformed by the proposed algorithms w.r.t. any time performance.
    % modularity clustering 
    \newline
    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
    best performance.
    The proposed methods performs reasonable, but  KL is faster and leads to better energies.
  }
  \label{fig:anytime}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-14 paper/egpaper_for_review.tex
fixed all changes where i knew the fix up tp parameter choise

\section{Future Work}\label{sec:future}
In future work we would like to investigate in much larger problem instances
and interactive correlation clustering, by enforcing
updates only in local regions by appropriate proposals.
%
Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
If those build a closed surface, the problem decompose into two independent problems.
%
Overall, a more specific selection of proposals, maybe conditioned on the current solution,
should lead better proposals and to faster progress of CC-Fusion.
%
Furthermore, we can extend our approach to higher-order correlation clustering~\cite{Kim-2011,kappes_2013_arxiv}
by using higher order subproblems.

@@

We have presented a fast and scalable 
approximate solver for correlation 
clustering, named Correlation Clustering Fusion (CC-Fusion).
It is orthogonal to previous research, \ie it can be combined with and
correlation clustering solver.
%
The best solution is iteratively improved 
by a fusion with proposal solutions.
The fusion move itself is formulated as correlation
clustering on a smaller graph fewer edges and nodes
and can therefore be solved much faster than the original problem.

Our evaluation shows that several CC-Fusion
outperforms state-of-the-art solvers w.r.t. any time performance 
with increasing problem size.

>>>>

\section{Future Work}\label{sec:future}
In future work we would like to investigate in much larger problem instances
and interactive correlation clustering, by enforcing
updates only in local regions by appropriate proposals.
%
Within this challenging task we can also enforce additionally must-not-link constraints in eq.~\ref{eq:fusion_move_a}.
If those build a closed surface, the problem decomposes into two independent problems.
%
Overall, a more specific selection of proposals, maybe conditioned on the current solution,
should lead better proposals and to faster progress of CC-Fusion.
%
Furthermore, we can extend our approach to higher-order correlation clustering~\cite{Kim-2011,kappes_2013_arxiv}
by using higher order subproblems.

@@

We have presented a fast and scalable 
approximate solver for correlation 
clustering, named Correlation Clustering Fusion (CC-Fusion).
It is orthogonal to previous research, \ie it can be combined with
correlation clustering solver.
%
The best solution is iteratively improved 
by a fusion with proposal solutions.
The fusion move itself is formulated as correlation
clustering on a smaller graph with fewer edges and nodes
and can therefore be solved much faster than the original problem.

Our evaluation shows that several CC-Fusion algorithms
outperforms state-of-the-art solvers w.r.t. any time performance 
with increasing problem size.

### 2014-11-14 paper/evaluation.tex
fixed all changes including page 5
fixed all changes where i knew the fix up tp parameter choise

\subsection{Evaluation}
For the evaluation of the diffrent methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evalution are given in supplementray material.

For \emph{social-nets} CC-Fusion methods provides for the first minutes the best results.
Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
MC-I and MC-R can even not be applied on such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generated would be a scalable implementations of the 
PIVOT algorithm.

For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even it 
and the used parameters was not designed and chosen for this type of problem.
Especially is does a better job than MC-I.

For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because, the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, with best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.

For the \emph{knott-datasets} similar holds as for image-seg. 
With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the global optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first usefull solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a view minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

>>>>

%!TEX root = ./egpaper_for_review.tex
\subsection{Evaluation}
For the evaluation of the different methods on the datasets introduced in Sec.~\ref{sec:datasets},
we show zoomed anytime plots in  Fig.~\ref{fig:anytime} and variation of information (VOI)~\cite{meila-2003}
and rand index (RI)~\cite{rand-1971} of the final solutions in Tab.~\ref{tab:eval}.
Anytime plots with no zooming and a detailed evaluation are given in supplementary material.

For \emph{social-nets} CC-Fusion methods provide the best results for the first minutes .
Only CGC and HC-CGC are able to find better solutions after more than 1000 seconds.
MC-I and MC-R can not be applied to such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generator would be a scalable implementation of the 
PIVOT algorithm.

For \emph{modularity-clustering} CC-Fusion performs on par to competitive methods, even CC-Fusion 
and the used parameters have not been designed and chosen for this type of problem.
Especially it does a better job than MC-I.

For \emph{image-seg} CC-Fusion is faster than other methods and competitive in terms of energy, VOI, and RI.
Because  the models are designed to have a high boundary recall (oversegmentation), 
classical fusion, which return undersegmentations, is best best VOI but worse RI and energy.
Proposals generated by EHC seemed to be a bit better than WS-based ones.

For the \emph{knott-datasets} similar holds as for image-seg. 
With increasing problem size CC-Fusion-HC-MC and CC-Fusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VOI and RI they are only slightly worse than the globally optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first useful solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a few minutes  CC-Fusion-HC-MC and CC-Fusion-WS-MC give much better results and also overall best in terms of energy, VOI, and RI.
%
Pure EHC, Fusion and PIVOT-BOEM do not give useful results on any dataset.
